---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(magrittr)
library(stringr)
library(targets)
```

# Overview

Project to facilitate phenotype extraction from the UK Biobank dataset. Please see [project website](https://rmgpanw.gitlab.io/ukb_extract_phenotypes) for further details.

# Setup

- Create an R script called `_targets_config.R` in the project root directory with the following objects and populate:

```{r results='asis', eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
result <- readLines(tar_read(TARGETS_CONFIG)) %>%
  # subset for comments, object assignments and empty lines
  subset(.,
         str_detect(.,
                    "^#+ |<-|^$")) %>%

  # remove assignments, leaving only object names
  str_replace("<-.*$",
              "<-") %>%

  # print
  paste(sep = "",
        collapse = "\n")

cat(paste0("```",
           "\n",
           result,
           "\n",
           "```"))
```

- Install required R packages with `renv::restore()`
- Run [targets pipeline](https://books.ropensci.org/targets/) with `tar_make()` in the R console, or using the 'Build' tab in RStudio.
